Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-05-11 krs-survey.tex
Filled section on TBox alteration

In systems

All systems allow to modify the ABox, not always possible to alter the TBox

>>>>

The content of a knowledge base is often conveniently divided into a
\emph{structural part} that defines the conceptualisation of a domain in term
of vocabulary and relations within the concepts, and an \emph{instantiation} of
this structure into concrete entities.

The terms TBox and ABox are commonly found to describe this two different types of
statements in ontologies. TBox statements describe a system in terms of
controlled vocabularies, for example, a set of classes and properties. ABox are
TBox-compliant statements about that vocabulary.

All knowledge representation systems allow to modify the ABox, which can be
considered as the dynamic part of the knowledge base. It is however not always
possible to alter the TBox because not all reasoning systems can dynamically
take into account structural changes in the knowledge base.

Example of TBox alteration include modification of the taxonomy (like addition
or retractation of a \concept{subClassOf} relation), changes to the asserted
domain or range of a predicate, addition or retractation of rules.

Supporting TBox alteration has notable consequences on the learning
capabilities of the system: teaching general facts (\ie, facts at the level of
whole categories) like ``cars go on roads'' to a robot requires an alteration
of the TBox.
